---
title       : Marketing analysis study of household incomes
subtitle    : Sunday, May 24, 2015
author      : Michael
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
<style type='text/css'>
img {
    max-height: 360px;
    max-width: 664px;
}
</style>

## Study overview
* A survey was conducted in to determine demographic attributes that influence household income.  

* 8,993 observations and 14 variables were collected (during the 1987 study in San Francisco) and included in the analysis.  Key variables include the following: Income, Sex, Marital status, Age, Education, Occupation, Years living in San Francisco, Dual Income, Household count, Household count under 18, Homeowner Status, Home type, Ethnic, and language.

* Data is compiled and simple analysis performed via histogram plotting.  

```{r, echo=FALSE}
library(ElemStatLearn)
library(ggplot2)
data(marketing)
df <- subset(marketing, marketing$Income=="7")
Income <- df$Income
Age <- gsub("^1","14-17",df$Age)
Age <- gsub("^2","18-24",Age)
Age <- gsub("^3","25-34",Age)
Age <- gsub("^4","35-44",Age)
Age <- gsub("^5","45-54",Age)
Age <- gsub("^6","55-64",Age)
Age <- gsub("^7",">65",Age)
temp <- cbind(Income, Age)
temp <- as.data.frame(temp)
temp <- subset(temp, select=c("Age"))
colnames(temp) <- c("type")
temp <- subset(temp, temp[,1]!="NA")
```

--- .class #id

## ShinyApp to view Market survey analysis
* ShinyApp server and user interface can be used to conveniently cycle through data parameters making it easy to distinguish key variables contributing to household income.  

* Simply select an attribute from the attribute menu and select a household income range and a histogram plot is generated within seconds.  

* Quickly compare new variables... clicking another parameter(radio button) will automatically update the histogram to your selection.  


--- .class #id 

## Example plot generated from Shinyapp
```{r, echo=TRUE}
g <- ggplot(temp, aes(type))
g + geom_histogram(aes(fill=type), stat = "bin") + labs(title = paste("$40k-$50k 
Annual Household Income")) + guides(fill=guide_legend(title="Age")) + 
  theme(axis.text.x = element_text(angle = 30, vjust = 0.5, size = 12))
```


--- .class #id

## Conclusion
* ShinyApp provides added convenience for the market analysis study.  

* 13 variables with 9 choices of household income adds up to 100+ total plots.  ShinyApp makes data analysis enjoyable with one interactive plot.  

* Stay focused on analysis with all market analysis data accessible at once.  

* https://datasci14.shinyapps.io/datasci14/




